---
title: "gapminder-analysis"
author: "victoria lloyd"
date: "10 April 2019"
output: 
   html_document: 
    toc: true 
    toc_float: true
    theme: cerulean
    highlight: zenburn
---

### Introduction to gap minder

With the Ignorance Project we identify the specific global statistical trends that have not reached a broad public audience. 

```{r, chunk-label, fig.height=4}
print("hello world")
```
 eval = false, print chunk but wont evaluate, eg.g when you are installing packages
  echo = false, run the code but don't show me the code 
  
  # gap minder download package
  
  install gapminder package
  
```{r, eval=FALSE}
install.packages("gapminder")
```
  
  also install skimr, plotly, DT
  
```{r, eval=FALSE}
install.packages(c("skimr", "plotly", "DT"))
```
  
  plot 
```{r}
library(gapminder)
gapminder
```
  
  
```{r}
library(ggplot2)
p <- ggplot(gapminder, aes(x= gdpPercap, y = lifeExp, color = continent))+
  geom_point()
p
```
  
```{r}
library(plotly)
ggplotly(p)
```
  
  